Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-02-02 paper-webserver.tex
DEBUG: figures are everywhere
CHANGE: rewrote the intro for the Discussion section to focus on data storage / speed, as opposed to the analysis pipelines

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/ontology}
\end{center}
\caption{Caption for figure within column.}
\label{fig-ontology}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/results.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-results}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/tables.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-tables}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/docker}
\end{center}
\caption{Caption for figure within column.}
\label{fig-docker}
\end{figure}

\subsection{Continuous integration and testing}
% Keep this short
% para
% 1. goals: why CI, testing is important
% 2. how we've implemented it, integration with github

@@

% analysis run-time / throughput with different levels of parallelization

@@

One of the key goals in developing Spfy is to maintain instantaneity, as modern websites have accustomed users to immediate results.
We attempt to use innovations in web development to bring a similar experience to Spfy as a predictive genomics platform for \textit{E. coli}.
The use of Docker containerization, task queues, and a graph database, were all chosen to support instantaneity; modern analytics platforms must respond to user-requested analyses of big-data in the same efficiency as old analyses of single files.

>>>>

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/ontology}
\end{center}
\caption{Caption for figure within column.}
\label{fig-ontology}
\end{figure}

@@

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/results.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-results}
\end{figure}

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/tables.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-tables}
\end{figure}

No account creation is required to use the platform. A sharable token is automically created for users upon opening the website, and is embeded into the website address. Users can share results with their colleagues by copying the url, and files can be submitted for analysis from different computers with results reflected on each others' screens.

@@

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/docker}
\end{center}
\caption{Caption for figure within column.}
\label{fig-docker}
\end{figure}

\subsection{Continuous integration}
% Keep this short
% para
% 1. goals: why CI, testing is important
% 2. how we've implemented it, integration with github

@@

% analysis run-time / throughput with different levels of parallelization
% particularly for statistical tests
% should do a 1 genome = X number VFs, Y number of genomes for Y*X retrieval/analysis

@@

One of the key goals in developing Spfy was to accomadate a variety of result formats, from storing subtyping data to retrieving results as inputs for downstream analyses, such as statistical significance testing. We've shown how a graph database can accomdate a variety of programs used by bioinformaticians and is performant for data retrieval on the results of 10,000+ genomes. Spfy maintains instantaneity, as modern analytics platforms must respond to user-requested analyses of big-data in the same efficiency as old analyses of single files.
